Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-25 02_Paper/paper.tex
Update sections: meeting 201125 Moritz and prz

\usepackage[bookmarks=false]{hyperref}
    \hypersetup{colorlinks,
      linkcolor=blue,
      citecolor=blue,
      urlcolor=blue}
\usepackage{xcolor}
\newcommand{\AP}[1]{{\color{blue} {\bf (AP: #1)}}}
\newcommand{\LS}[1]{{\color{purple} {\bf (LS: #1)}}}
\newcommand{\MW}[1]{{\color{teal} {\bf (MW: #1)}}}
\newcommand{\JG}[1]{{\color{green} {\bf (JG: #1)}}}
\newcommand{\DSt}[1]{{\color{orange} {\bf (DSt: #1)}}}

@@

\AP{ @Moritz: Why is figure 2 within the area of the Demozelle section?}

\section{Methods} %3/4 Page

Data  is collected from the demonstration cell and analyzed.

\subsection{Measurement}
\DSt{
- what is this section about?
}

\subsection{Machine Learning}
We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction.

@@

\subsection{Classifier optimization and testing}\label{sec:ml_exp}
The robot's position at disc drop is marked in 
Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
framed as a classification task. The input vectors which we feed into our
classifiers consists of the arm positions at the disc drops for both
discs in three dimensions, as well as the largest recorded belt speed
of all three belts. The interpretation of the quality measurement is 
used as the training target. It can be good or bad which we encode as 
zero and one.

@@

- Connection problem between devices
   - Network connection
   - Device restriction: SIM4000, SIEMENS. 
   - Server Timestamp syncr.
- Missing data tags: modifying PLC and robot code to have tags
- Interpretation of data: preprocessing
   - What data is relevant?
- Data sample size
- ML implementation @Moritz

>>>>

\usepackage[bookmarks=false]{hyperref}
    \hypersetup{colorlinks,
      linkcolor=blue,
      citecolor=blue,
      urlcolor=blue}
\usepackage{xcolor}
\newcommand{\AP}[1]{{\color{blue} {\bf (AP: #1)}}}
\newcommand{\LS}[1]{{\color{purple} {\bf (LS: #1)}}}
\newcommand{\FS}[1]{{\color{cyan} {\bf (FS: #1)}}}
\newcommand{\MW}[1]{{\color{teal} {\bf (MW: #1)}}}
\newcommand{\JG}[1]{{\color{green} {\bf (JG: #1)}}}
\newcommand{\DSt}[1]{{\color{orange} {\bf (DSt: #1)}}}

@@

\section{Machine Learning Methods} %3/4 Page

We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction.

@@

\subsection{Classifier optimization and testing}\label{sec:ml_exp}

The robot's position at disc drop is marked in 
Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
framed as a classification task. The input vectors which we feed into our
classifiers consists of the arm positions at the disc drops for both
discs in three dimensions, as well as the largest recorded belt speed
of all three belts. The interpretation of the quality measurement is 
used as the training target. It can be good or bad which we encode as 
zero and one.

@@

- Connection problem between devices
   - Network connection
   - Device restriction: SIM4000, SIEMENS. 
   - Server Timestamp syncr.
- Interpretation of data: preprocessing
   - What data is relevant?
   - Missing data tags: modifying PLC and robot code to have tags -> key point
        - Without label we cannot use supervised ML methods
- Dataset size
- ML implementation @Moritz
